Ms 1

### 2017-08-10 ms1/ms1_display.Rmd
ms1 display update

n_unique_bene = scan('tables/n_unique_bene.tsv')
n_million_unique_bene = round(scan('tables/n_unique_bene.tsv') / 1e6, 2)
n_million_pde = claims_by_abx %$% sum(n) %>% { round(. / 1e6, 2) }

@@

total_adjusted_change_str = model_abx %>%
  filter(term=='year0', antibiotic=='overall') %$%
  change_str

azithro_adjusted_change_str = model_abx %>%
  filter(term=='year0', antibiotic=='azithromycin') %$%
  change_str

levo_adjusted_change_str = model_abx %>%
  filter(term=='year0', antibiotic=='levofloxacin') %$%
  change_str
```

There are `r n_million_unique_bene` million unique beneficiaries and `r n_million_pde` million PDEs across all study years. Adjusted total consumption changed by `r total_adjusted_change_str` per year. Azithromycin changed by `r azithro_adjusted_change_str` per year. Levofloxacin changed by `r levo_adjusted_change_str` per year.

@@

@@

# but "overall" should not be in the claims_by_abx list
if('overall' %in% claims_by_abx$antibiotic) stop()

@@

x %>%
  ggplot(aes(x=antibiotic, y=pct_change, ymin=ci_low, ymax=ci_high)) +
  geom_bar(stat='identity', fill=NA, color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  ggtitle('Adjusted changes in consumption') +
  xlab('') +
  ylab('adjusted yearly change in claims per beneficiary per year') +
  scale_y_continuous(limits=c(-10, 10), breaks=c(-10, -5, 0, 5, 10)) +
  theme_minimal()
```

```{r adjusted_changes_table}
x %>% arrange(desc(antibiotic)) %>% kable
```

@@

```{r fq}
read_tsv('tables/model_fq.tsv') %>%
  model_ci() %>%
  select(term, pct_change, ci_low, ci_high, p.value) %>%
  kable
```

Overall, fluoroquinolones changed by about 0% per year during this period.

@@

```{r dx_counts}
dx_counts = read_tsv('tables/dx_counts.tsv') %>%
  left_join(totals, by='year') %>%
  mutate(dx_pkb=round(n/n_bene*1000, 1)) %>%
  select(diagnosis_type, year, dx_pkb)

dx_counts_trends = dx_counts %>%
  group_by(diagnosis_type) %>%
  arrange(year) %>%
  summarize(p=round(trend_p(dx_pkb), 2))

dx_counts %>%
  spread(year, dx_pkb) %>%
  left_join(dx_counts_trends, by='diagnosis_type') %>%
  arrange(desc(`2011`)) %>%
  kable
```

@@

```{r dxrx_fraction}
dxrx_frac = read_tsv('tables/dxrx_fractions.tsv') %>%
  group_by(year, diagnosis_type) %>%
  mutate(total=sum(n)) %>%
  ungroup() %>%
  mutate(f=round(100*n/total, 1)) %>%
  filter(antibiotic %in% top_abx) %>%
  select(diagnosis_type, antibiotic, year, f) %>%
  spread(year, f) %>%
  filter(`2011` >= 5) %>%
  arrange(diagnosis_type, desc(`2011`))

>>>>

n_unique_bene = scan('tables/n_unique_bene.tsv')
n_million_unique_bene = round(scan('tables/n_unique_bene.tsv') / 1e6, 2)
n_pde = sum(claims_by_abx$n)
n_million_pde = round(n_pde / 1e6, 2)

@@

bind_rows(claims_by_abx, claims_overall) %>%
  filter(antibiotic %in% c('overall', 'azithromycin', 'levofloxacin'), year %in% c(2011, 2014)) %>%
  select(antibiotic, year, cpkp) %>%
  spread(year, cpkp) %>%
  mutate(pct_change=round(100*(`2014`-`2011`)/`2011`, 2)) %>%
  kable
```

There are `r n_million_unique_bene` million unique beneficiaries and `r n_million_pde` million PDEs across all study years.

@@

There were `r prettyNum(n_unique_bene, big.mark=',')` unique beneficiaries and `r prettyNum(n_pde, big.mark=',')` PDEs.

@@

@@

x %>%
  ggplot(aes(x=antibiotic, y=pct_change, ymin=ci_low, ymax=ci_high)) +
  geom_bar(stat='identity', fill=NA, color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted yearly change in consumption (%)') +
  scale_y_continuous(limits=c(-10, 10), breaks=c(-10, -5, 0, 5, 10)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))
```

```{r adjusted_changes_table}
x %>% arrange(desc(antibiotic)) %>% kable

adjusted_az_decrease = x %>%
  filter(antibiotic=='azithromycin') %$%
  { (1 + pct_change/100)^3 } %>%
  { (1 - .) * 100 } %>%
  round(2)

adjusted_levo_increase = x %>%
  filter(antibiotic=='levofloxacin') %$%
  { (1 + pct_change/100)^3 } %>%
  { (. - 1) * 100 } %>%
  round(2)
```

Consumption of azithromycin fell by `r adjusted_az_decrease`% over the entire study period. Levofloxacin consumption increased by `r adjusted_levo_increase`% over the entire study period.

@@

```{r fq}
fq_names = claims_by_abx %>%
  filter(str_detect(antibiotic, 'floxacin')) %>%
  group_by(antibiotic) %>%
  summarize(n=sum(n)) %>%
  arrange(desc(n)) %$%
  antibiotic

read_tsv('tables/model_fq.tsv') %>%
  model_ci() %>%
  select(term, pct_change, ci_low, ci_high, p.value) %>%
  kable
```

Overall, fluoroquinolones changed by about 0% per year during this period. This included `r fq_names`.

@@

```{r dx_counts}
dx_counts = read_tsv('tables/dx_counts.tsv') %>%
  left_join(totals, by='year') %>%
  mutate(dx_pkb=n/n_bene*1000) %>%
  select(diagnosis_type, year, dx_pkb)

dx_counts_trends = dx_counts %>%
  group_by(diagnosis_type) %>%
  arrange(year) %>%
  summarize(p=trend_p(dx_pkb))

dx_counts %>%
  spread(year, dx_pkb) %>%
  mutate(pct_change_per_year=(`2014`-`2011`)/`2011`*100/3) %>%
  left_join(dx_counts_trends, by='diagnosis_type') %>%
  arrange(desc(`2011`)) %>%
  mutate_at(vars(`2011`:p), function(x) round(x, 2)) %>%
  kable
```

@@

```{r dxrx_fraction}
dxrx_frac = read_tsv('tables/dxrx_fractions.tsv') %>%
  group_by(year, diagnosis_type) %>%
  mutate(total=sum(n)) %>%
  ungroup() %>%
  mutate(f=round(100*n/total, 1)) %>%
  filter(antibiotic %in% top_abx) %>%
  select(diagnosis_type, antibiotic, year, f) %>%
  spread(year, f) %>%
  filter(`2011` >= 3) %>%
  arrange(diagnosis_type, desc(`2011`))
